---
title: "Shiny-example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyexample)
```


# Introduction

The package `shinyexample` is made to help students make a project that includes a shiny app.

# Functions

You can use one file for each function if you wish -- although this might get a little messy if the number of function go past about 10.

It would be better to classify the function by what they do and then put all topic similar functions in one file.

## OOP

In this package we will be using `S3` OOP -- which is the commonly used object oriented form in R package making.

See <https://adv-r.hadley.nz/s3.html> for more information.

## Documentation

There should be two forms of documentation
  
  1. Function specific using Roxygen.
  2. Vignette -- long form.
  
# Constructor

The first function is `myttest` and it produces a list of useful information to be processed by method functions.

```{r}
a <- rnorm(40, 20, 10)
b <- rnorm(30, 10, 12)

out <- myttest(x=a, y=b, paired = FALSE)
class(out)
```


Notice that the output is of class `r class(out)`

The function returns a list of components:

```{r}
names(out)
```

The components can then be operated on by an appropriate method attached to a generic.

# Method

The method is attached to the generic finction `plot()`

```{r, eval=FALSE}
plot.mytt()
```



We can call it by simply invoking the `plot()` function

```{r}
plot(out)
```



# Shiny server

These two functions have been placed into a shiny app and can be invoked using 

```{r,eval = FALSE}
shinyhist()
```

